% build with lualatex, pass options by
%   lualatex "\def\option{1} \input{cv.tex}"
% where  option  is one of
%   includecoursework
%   includeearlyexp
%   includeextra
%   enfontname
%   zhfontname

\documentclass[11pt]{article}

\usepackage[letterpaper,total={7.2in,9.8in}]{geometry}
\usepackage{datetime2} % iso-format
\usepackage{fontspec}  % loading fonts (lualatex)
\usepackage{titlesec}  % customize \section
\usepackage{enumitem}  % customize \enum

% set fonts
%   requires: fontspec, installed fonts
\providecommand{\enfontname}{STIX Two Text}
\providecommand{\zhfontname}{Noto Serif CJK SC}
\setmainfont{\enfontname}
\newfontfamily\zhfont[Ligatures=TeX]{\zhfontname}
% switch off page numbering
\pagenumbering{gobble}
% font size and rule for section headings
% spacing around subsection headings
%   requires: titlesec
\titleformat{\section}{\scshape\large}{\thesection}{1em}{}[{\titlerule[0.1pt]}]
\titleformat*{\subsection}{\normalsize\bfseries}
\titlespacing\subsection{0pt}{10pt plus 2pt minus 1pt}{0pt}
% do not indent paragraphs
\setlength{\parindent}{0pt}
% remove vertical spacing between items
%   requires: enumitem
\setlist{noitemsep}

% subsection with additional text floating right
\newcommand{\subsec}[2]{\subsection*{#1 \hfill {\normalfont\itshape #2}}}
% a description line in italic
\newcommand{\subsecdesc}[2]{{#1 \hfill \itshape #2}}

\title{
  \bfseries\underline{Li} Yefeng
  (\raisebox{-1pt}{\Large\zhfont 李烨锋})}
\author{
  \normalsize li3915@purdue.edu \\
  \normalsize +1 765-409-7247}

\begin{document}

\maketitle

\section*{Research Interests} %-------------------------------------------------

  My research interests lie in the broad area of Programming Languages:
  theories of proofs, types, languages, and mathematics. I hope to develope
  rigorously founded theories and tools at the service of software
  reliability and human productivity.

\section*{Education} %----------------------------------------------------------

  \subsec{Purdue University}
         {West Lafayette, IN, USA}
  \subsecdesc{Ph.D. student in Computer Science. Focus: programming languages}
             {since 2021-01}

  \subsec{Hong Kong University of Science and Technology (HKUST)}
         {Hong Kong S.A.R.}
  \subsecdesc{M.Phil. in Computer Science and Engineering}
             {2018-09/2020-06} \\
  \subsecdesc{B.Eng. in Computer Engineering | Minor in Robotics}
             {2014-09/2018-06}

\ifdefined\includecoursework
\section*{Coursework} %----------------------------------------------------------

  Reasoning about Programs,
  Introduction to Advanced Algorithmic Techniques,
  Introduction to Combinatorial Optimization,
  Advanced Computer Graphics,
  Copmuter Communication Networks,
  System and Kernel Programming in Linux, etc.
\fi

\section*{Research Projects} %--------------------------------------------------

  \subsec{Probabilistic consistency model in distributed replicas}
         {PurPL, CS, Purdue University}
  \subsecdesc{Work in progress, advised by Prof. Suresh Jagannathan}
             {since 2021-02}
  \begin{itemize}
    \item The goal of this research is to provide a framework that helps
      distributed program developers identify a consistency model that
      provide probabilistic (soft) guarantees. Methods employed include
      probabilistic programming and Bayesian inference.
  \end{itemize}

  \subsec{Manifoldness preserving contraction}
         {VisGraph Lab, CSE, HKUST}
  \subsecdesc{M.Phil. thesis, advised by Prof. Quan Long}
             {2018-08/2020-05}
  \begin{itemize}
    \item Designed a new contraction method that guarantees manifold output
      given a manifold input using augmentation and the separation of
      singularities. It can be applied to geometry processing as a replacement
      to the conventional contraction operation which may destroy topology and
      produce imperfect results.
    \item Applied the new contraction method to improve triangle mesh
      simplification.
  \end{itemize}

  \subsec{Centralized Wireless Local Area Networks}
         {HKUST}
  \subsecdesc{Undergraduate final-year thesis, advised by Prof. Brahim Bensaou}
             {2017-09/2018-03}
  \begin{itemize}
    \item Specified a centralization protocol for Wireless LANs as an
      (SDN) extension atop CSMA/CA to explore the
      improvement of resource utilization in dense indoor networks. It was
      partially implemented in C based on hostapd's source code and experimented
      on OpenWrt embedded Linux system.
  \end{itemize}

\ifdefined\includeearlyexp
  \subsec{Photograph capturing with drones}
         {VisGraph Lab, CSE, HKUST}
  \subsecdesc{Undergraduate Research Opportunity Program, advised by Prof. Quan Long}
             {2016-08/2016-11}
  \begin{itemize}
    \item Investigated in the application of Computer Vision and Graphics for
      Android devices as remote controls for drones, with a focus on human-drone
      interaction. An Android application was built to retrieve data from a
      geography database and visualize useful information on the screen
      according to the vision of the drone.
  \end{itemize}
\fi

\section*{Professional Experience} %--------------------------------------------

  \subsec{Everest Innovation Technology \small{(merged into Apple Inc.)}}
         {Shenzhen \& Hong Kong, China}
  \subsecdesc{Researcher \& software developer}
             {2019-06/2019-08}
  \begin{itemize}
    \item \textbf{Triangle mesh processing}: Transferred novel geometry
      processing techniques into \emph{Altizure}, a world-class cloud-based 3D
      reconstruction platform; developed efficient mesh processing program in
      C++.
    \item \textbf{ZRPC}: Participated in the development of \emph{ZRPC}, an RPC
      distributed computing framework, in Go.
    \item \textbf{Data management and visualization}: Developed a photographic
      data validation, management, and visualization desktop application in
      JavaScript.
  \end{itemize}

\ifdefined\includeearlyexp
  \subsec{Dash Serviced Suites}
         {Hong Kong}
  \subsecdesc{Part-time JavaScript developer}
             {2018-02/2018-05}
  \begin{itemize}
    \item \textbf{Web development}: Worked on the Web interface, API, and
      database management of \emph{DASH2}, an online marketplace Web application
      by the startup company.
  \end{itemize}
\fi

\section*{Teaching Experience} %------------------------------------------------

  \subsec{Department of Computer Science, Purdue University}
         {West Lafayette, IN, USA}
  \subsecdesc{Teaching assistant for CS24000: Programming in C}
             {Spring 2021}
  \subsec{Department of Computer Science and Engineering, HKUST}
         {Hong Kong}
  \subsecdesc{Teaching assistant for COMP1021: Introduction to Computer Science}
             {Fall 2019} \\
  \subsecdesc{Teaching assistant for COMP3311: Database Management Systems}
             {Fall 2018}

\ifdefined\includeextra
\section*{Extracurricular Activities} %-----------------------------------------

  \subsec{ACM SIGPLAN Symposium on Principles of Programming Languages}
         {New Orleans, LA, USA}
  \subsecdesc{Student Volunteer}
             {2020-01}
  \begin{itemize}
    \item Supported event organization.
  \end{itemize}

  \subsec{RoboMaster Robotics Competition}
         {Shenzhen, China}
  \subsecdesc{Mechanical/Computer Engineer}
             {2017-02/2017-08}
  \begin{itemize}
    \item Co-designed the mechanical structure of \emph{Hero}, the main-force in
      this multi-robot contest, for RoboMaster HKUST team. Our Hero robot was
      controlled remotely, capable of capturing, storing and shooting bullets,
      and climbing onto stairs with telescopic legs.
  \end{itemize}

  \subsec{Chinese Folk-Art Society, HKUST}
         {Hong Kong}
  \subsecdesc{IT Secretary, Executive Committee}
             {2015-02/2016-02}
  \begin{itemize}
    \item Independently built the official website of our society and developed
      a Web application in JavaScript to assist the hosting of a knowledge
      competition named \emph{Who is Still Standing}.
    \item Took charge of photographing and Internet platform promotions.
    \item Organized trips to the Yangzi, China and Dragon's Back, Hong Kong.
  \end{itemize}
\fi

\end{document}
