\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{xeCJK}
\usepackage{fontspec}
\setmainfont[Ligatures=TeX]{Linux Libertine O}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large LI Yefeng (zh: 李烨锋)} &
   \href{mailto:li3915@purdue.edu}{li3915@purdue.edu} \\
  & +852 56895775 or +86 13238191225 \\
\end{tabular*}


%----------- Education -----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Purdue University}{West Lafayette, IN, USA}
      {Doctor of Philosophy student in Computer Science}{Incoming}
    \resumeSubheading
      {Hong Kong University of Science and Technology (HKUST)}{Hong Kong S.A.R.}
      {Master of Philosophy in Computer Science and Engineering}{Sep. 2018 -- June 2020}
    \resumeSubheading
      {Hong Kong University of Science and Technology}{Hong Kong S.A.R.}
      {Bachelor of Engineering in Computer Engineering; Minor in Robotics}{Sep. 2014 -- June 2018}
  \resumeSubHeadingListEnd
  
%----------- Research Experience -----------------
\section{Research}
\resumeSubHeadingListStart

  \resumeSubheading
    {VisGraph Lab, CSE, HKUST}{Hong Kong}
    {M.Phil. student; advised by Prof. Quan Long}
    {Aug. 2018 -- May 2020}
    \resumeItemListStart
      \resumeItem{Manifoldness Preserving Contraction (M.Phil. thesis)}{
        Designed a new contraction method that guarantees manifold output given a manifold input by augmentation and the separation of singularities. It can be applied to geometry processing as a replacement to the conventional contraction operation which may destroy topology.}
      \resumeItem{Triangle mesh simplification}{
        Used new contraction techniques to improve triangle mesh simplification; facilitated the parallelization in Levels-of-Detail generating process using 2D-projection of tile boundaries.}
    \resumeItemListEnd
    
  \resumeSubheading
    {HKUST}{Hong Kong}
    {Undergraduate final-year student; advised by Prof. Brahim Bensaou}
    {Sep. 2017 -- Mar. 2018}
    \resumeItemListStart
      \resumeItem{Centralized Wireless Local Area Networks (final-year thesis)}{
        Specified a centralization protocol for Wireless LANs as an (software-defined networking) extension atop CSMA/CA to explore the improvement of resource utilization in dense indoor networks. It was partically implemented in C based on hostapd's source code and experimented on OpenWrt embedded Linux system.}
    \resumeItemListEnd
    
  \resumeSubheading
    {VisGraph Lab, CSE, HKUST}{Hong Kong}
    {Undergraduate Research Opportunity Program participant; advised by Prof. Quan Long}
    {Aug. -- Nov. 2016}
    \resumeItemListStart
      \resumeItem{Photograph capturing with drones}{
        Investigated in the application of Computer Vision and Graphics for Android devices as remote controls for drones, with a focus on human-drone interaction.}
    \resumeItemListEnd

\resumeSubHeadingListEnd
  
%----------- Industrial Experience -----------------
\section{Industrial}
\resumeSubHeadingListStart

  \resumeSubheading
    {Everest Innovation Technology \small{(now acquired by Apple Inc.)}}{Shenzhen \& Hong Kong, China}
    {Researcher and Software Developer}
    {June. -- Aug. 2019}
    \resumeItemListStart
      \resumeItem{Triangle mesh processing}{
        Transferred novel geometry processing techniques into \emph{Altizure}, a world-class cloud-based 3D reconstruction platform; developed efficient mesh processing program in C++.}
      \resumeItem{ZRPC}{
        Participated in the development of \emph{ZRPC}, an RPC distributed computing framework, in Go.}
      \resumeItem{Data management and visualization}{
        Developed a photographic data validation, management, and visualization desktop application in JavaScript.}
    \resumeItemListEnd
    
  \resumeSubheading
    {Dash Serviced Suites}{Hong Kong}
    {Part-time JavaScript Developer}
    {Feb. -- May 2018}
    \resumeItemListStart
      \resumeItem{Web development}{Worked on the Web interface, API, and database management of \emph{DASH2}, an online marketplace Web application.}
    \resumeItemListEnd

\resumeSubHeadingListEnd
  
%----------- Teaching Experience -----------------
\section{Teaching}
\resumeSubHeadingListStart

  \resumeSubheading
    {COMP1021: Introduction to Computer Science, HKUST}{Hong Kong}
    {Teaching Assistant}
    {Sep. -- Dec. 2019}

  \resumeSubheading
    {COMP3311: Database Management Systems, HKUST}{Hong Kong}
    {Teaching Assistant}
    {Sep. -- Dec. 2018}

\resumeSubHeadingListEnd
  
%----------- Teaching Experience -----------------
\section{Extracurricular}
\resumeSubHeadingListStart

  \resumeSubheading
    {ACM SIGPLAN Symposium on Principles of Programming Languages}{New Orleans, LA, USA}
    {Student Volunteer}
    {Jan. 2020}
    \resumeItemListStart
      \item Supported event organization.
    \resumeItemListEnd

  \resumeSubheading
    {RoboMaster Robotics Competition}{Shenzhen, China}
    {Mechanical/Computer Engineer}
    {Feb. -- Aug. 2017}
    \resumeItemListStart
      \item Co-designed the mechanical structure of \emph{Hero}, the main-force in this multi-robot contest, for RoboMaster HKUST team. Our Hero robot was controlled remotely, capable of capturing, storing and shooting bullets, climbing onto stairs with telescopic legs.
    \resumeItemListEnd

  \resumeSubheading
    {Chinese Folk-Art Society, HKUST}{Hong Kong}
    {IT Secretary, Executive Committee}
    {Feb. 2015 -- Feb. 2016}
    \resumeItemListStart
      \item Independently built society's official website and developed a Web application in JavaScript to assist hosting knowledge competition \emph{Who is Still Standing}.
      \item Took charge of photographing and online platform promotions.
      \item Organized trips to the Yangzi, China and Dragon's Back, Hong Kong.
    \resumeItemListEnd

\resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
